---
title: "final_LTER_proj"
format: html
editor: visual
---

Libraries

```{r}
library(tidyverse)
library(skimr)
library(tidytext)
library(here)
library(ggplot2)
library(janitor)


```

-   Read in both files (ice cover duration and meteorological data). Note that the ice cover data has some NA values stored as -999.

```{r}
icedata <- read_csv(here::here("data", "meteor.csv" ), na = c("-999")) %>%
  clean_names()


lale <- read_csv(here::here("data", "lakes.csv"), na = c("-999")) %>%
  clean_names()
```

-   Create a visualization that compares ice duration across different lakes in the Madison Lake Area. Include both the actual ice duration values *and* some representation of summary statistics for each lake. Careful if you use a boxplot over a jitter or beeswarm - what values might be doubly represented? Can you find an argument that would help you remove those from the boxplot?

```{r}
ggplot(data = lale, aes(x = lakeid, y = editlale)) +
  geom_boxplot() +
  geom_line(data = editlale)

```

```{r}
editlale <- lale %>%
  group_by("lakeid") %>%
  summarize(mean_duration = mean(ice_duration, na.rm = TRUE),
            sd_duration = sd(ice_duration, na.rm = TRUE))
  
```

```{r}
ggplot(data = lizards, aes(x = total_length, y = weight, colour = common_name)) +
  geom_point() +
  facet_wrap(~ common_name, scales =
               
    
               
```
